Combining information from photometric and spectroscopic data:\\ Don't waste your time in spectrophotometric calibration!

### 2014-07-07 tex/ms.tex
moving some model description text around
more about the mean model

The data we use to test our method consists of optical spectroscopy of
XX stellar clusters in M31 for which YY-band HST photometric data
exist.  The optical spectra were obtained using the fiber-fed
Hectoscpec intrument on MMT by \citet{caldwell}.  The wavelength range
of the spectra is $3700-7200 \AA$. The instrumental resolution is
$\sim 5\AA$ across the optical range \citep{fabricant13}.  Wavelength
calibration happened. Sky subtraction happened. The data were
approximately spectrophotometrically calibrated using an average
calibration vector the night constructed from.... (MORE HERE). Figure
\ref{fig:data} shows the spectra before and after calibration for each
cluster.  Discuss S/N, sky subtraction.

\subsection{Star Cluster Model}
We model the stellar cluster as a single age SSP. The spectrum of a
star cluster under this assumption is given by
\begin{eqnarray}\displaystyle
F_{\theta^\prime}(\lambda_o) & = &
\frac{m_*}{4\pi d_L^2(1+z)} \, S(\lambda, t, Z , \beta) \, e^ {-k_\lambda\tau_V} \\
\nonumber \\ 
\lambda_o & = & (1+z)\,\lambda 
\\
\theta^\prime & \equiv & \left[ m_*, t, Z, \tau_V, z, d_L, \beta \right]
\quad ,
\end{eqnarray} where the
parameters $\theta^\prime$ include the stellar mass $m_*$, effective optical
depth to dust in the $V$-band $\tau_V$, luminosity distance $d_L$,
and redshift $z$.  The obsrved frame wavelengths $\lambda_o$ are
related to the restframe wavelengths $\lambda$ in the usual way.

The spectrum of one solar mass of stars that formed at lookback time
$t$ with metallicity $Z$ is given by $S(\lambda, t, Z [, \beta])$.
Here the additional parameters $\beta$ may include details of the
population synthesis model, such as the IMF slope and adjustments to
the stellar spectra or stellar evolutionary tracks
\citep[e.g.][]{FSPS}. We will assume $\beta$ to be fixed for the
purposes of this exercise, with no loss of generality (KEEPING IMF
SLOPE CONSTANT FOR NOW).  We will also fix the shape of the
attenuation curve, $k_\lambda \equiv \tau_\lambda/\tau_V$, to the Milky
way average of \citet{CCM89} with $R_V=3.1$ and assume that $d_L$ is
known to high precision from independent methods.

BDJ Discuss broadening here.  The instrumental resolution is given by $\sigma$,

@@

We calculate $S(\lambda, t, Z)$ using the Flexible Stellar Population
Synthesis code \citep[FSPS][]{FSPS}.  We use the Padova isochrones
\citep{Padova} and the MILES stellar spectral library \citep{MILES}.  The model
spectra are smoothed by convolution with a Gaussian in wavelength
space (to model the MMT line-spread function) and are interpolated to
the wavelength points of the of the observed spectrum while taking
into account the redshift.

>>>>

The data we use to test our method consists of optical spectroscopy of
XX stellar clusters in M31 for which YY-band HST photometric data
exist.  The optical spectra were obtained using the fiber-fed
Hectoscpec intrument on MMT by \citet{caldwell}.  The wavelength range
of the spectra is $3700-7200 \AA$. The instrumental resolution is
$\sim 5\AA$ across the optical range \citep{fabricant13}.  Wavelength
calibration happened. Sky subtraction happened. The data were
approximately spectrophotometrically calibrated using an average
calibration vector for the night constructed from.... (MORE HERE). Figure
\ref{fig:data} shows the spectra before and after calibration for each
cluster.  Discuss S/N, sky subtraction.

\subsection{Star Cluster Model}
We model the stellar cluster as a single age SSP. The spectrum of a
star cluster under this assumption is given by
\begin{eqnarray}\displaystyle
F_{\theta^\prime}(\lambda_o) & = &
\frac{m_*}{4\pi d_L^2(1+z)} \, S(\lambda, t, Z , \beta) \, e^ {-k_\lambda\tau_V} \\
\nonumber \\ 
\lambda_o & = & (1+z)\,\lambda 
\\
\theta^\prime & \equiv & \left[ m_*, t, Z, \tau_V, z, d_L, \beta \right]
\quad ,
\end{eqnarray} where the
parameters $\theta^\prime$ include 
the stellar mass $m_*$, 
effective optical depth to dust in the $V$-band $\tau_V$, 
luminosity distance $d_L$,
and redshift $z$.  
The observed frame wavelengths $\lambda_o$ are related to the restframe
wavelengths $\lambda$ in the usual way.

The spectrum of one solar mass of stars that formed at lookback time
$t$ with metallicity $Z$ is given by $S(\lambda, t, Z [, \beta])$.
Here the additional parameters $\beta$ may include details of the
population synthesis model, such as the IMF slope and adjustments to
the stellar spectra or stellar evolutionary tracks. We will assume
$\beta$ to be fixed for the purposes of this exercise, with no loss of
generality (KEEPING IMF SLOPE CONSTANT FOR NOW).  We will also fix the
shape of the attenuation curve, $k_\lambda \equiv
\tau_\lambda/\tau_V$, to the Milky way average of \citet{CCM89} with
$R_V=3.1$ and assume that $d_L$ is known to high precision from
independent methods and can therefore be treated as fixed.  In
practice, $d_L$ is completely degenerate with $m_*$. We calculate
$S(\lambda, t, Z)$ using the Flexible Stellar Population Synthesis
code \citep[FSPS][]{FSPS}.  We use the Padova isochrones
\citep{Padova} and the MILES stellar spectral library \citep{MILES}.

BDJ IMPROVE DISCUSSION OF BROADENING.  The model spectra are smoothed
by convolution with a Gaussian in wavelength space (to model the MMT
line-spread function) and are interpolated to the wavelength points of
the of the observed spectrum while taking into account the
redshift. The instrumental resolution is given by $\sigma$.

@@
